Untitled Vaccine Intuitive theories paper

### 2021-07-18 paper/paper.Rmd
added ref

Even before the coronavirus pandemic, misconceptions about vaccine safety drove public health crises around the world. Undervaccination resulted in outbreaks of measles affecting over 1000 children across the United States in 2019, and over 80,000 children across Europe in 2018 (WHO, 2018). Misconceptions about childhood vaccination---particularly the fraudulent claim that vaccines cause autism or other dangerous side-effects---have proved remarkably difficult to correct [e.g., @betsch.sachse2013; @horne.etal2015]. Sadly, only a handful of educational interventions have been found to improve vaccine attitudes [e.g., @horne.etal2015; @vannice.etal2011; @wallace.etal2006; @dube.etal2015]. This is especially  sobering in the context of the coronavirus pandemic: reluctance to be vaccinated against COVID-19 threatens our ability to end a pandemic that has already claimed millions of lives around the world.

>>>>

Even before the coronavirus pandemic, misconceptions about vaccine safety drove public health crises around the world. Undervaccination resulted in outbreaks of measles affecting over 1000 children across the United States in 2019, and over 80,000 children across Europe in 2018 [@thornton2019]. Misconceptions about childhood vaccination---particularly the fraudulent claim that vaccines cause autism or other dangerous side-effects---have proved remarkably difficult to correct [e.g., @betsch.sachse2013; @horne.etal2015]. Sadly, only a handful of educational interventions have been found to improve vaccine attitudes [e.g., @horne.etal2015; @vannice.etal2011; @wallace.etal2006; @dube.etal2015]. This is especially  sobering in the context of the coronavirus pandemic: reluctance to be vaccinated against COVID-19 threatens our ability to end a pandemic that has already claimed millions of lives around the world.
